\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
added summary for CEN.

So, the Central Executive Network is involved in

cultivate their abilities to
monitor cognitive processes related to attention and distraction, making them well suited to
report on these mental events.
\todo{Summarize CEN? Relevance to meditation?}

>>>>

So, the Central Executive Network is involved in goal-directed behavior and processes 
related to attention. These goals are usually external and attention is also directed externally(whether 
voluntary or not). When you meditate, you direct your attention voluntarily
inside, to the same sensory cues that are directing the PPC.
When you meditate, you also cultivate your cognitive processes related to attention.
When your wanders, you notice it and bring it back.

\todo{Summarize CEN? Relevance to meditation?}
